mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-02-14 EMSOFT2016/thesis.tex
update

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
Multitasking's execution time is about the same as singletasking's while co-routine takes more time than them to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.

@@

Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
Each execution time of cyclic period is the same as the others.
That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.

>>>>

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
The overhead of multitask is about 5 \% ($(multitask-singletask)/multitask$).
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
The scheuler interrupts and switches tasks, which causes this overhead.

@@

Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
Each execution time of cyclic period is the same as the others.
That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
%because of the low overhead.

### 2016-02-14 thesis/thesis.tex
update

When {\it rotateReadyQueue} is called, tasks with the same priority are switched.
The argument of {\it rotateReadyQueue} is the priority.

@@

\chapter{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.

>>>>

When {\it rotateReadyQueue} is called, tasks with the same priority are switched as shown in Figure \ref{fig:rotateReadyQueue}.
The argument of {\it rotateReadyQueue} is the priority.

@@

\chapter{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
%because of the low overhead.
